Pancreatic endocrinogenesis

### 2024-07-30 nbs/tutorials/pancreas/pancreas.qmd
feat(nbs): initialize downsampled pancreas tutorial
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Interactive results review
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

@@

@@

::: {#wrn-simulated-data .callout-warning collapse=true title="Simulated Data"}
In this notebook we illustrate how to download and review results using
unrealistic simulated data. Therefore, nothing in this notebook should be taken
to represent the results of applying the model to real data.
:::

@@

When testing or prototyping it is helpful to review the results of a workflow
execution interactively. This is relatively straightforward when working with locally
executed workflows as demonstrated in
[Usage](/templates/user_example/user_example.qmd).
However it is increasingly the case that the data set sizes and model training
resources will not be available or accessible locally, we would like to be able to interactively review results even when they have been computed in a remote cluster with sufficient resources.

In this guide we therefore illustrate working with the results 
of workflows that have been executed remotely. In this particular case, GitHub 
OAuth access is required to the endpoint associated to the workflow execution.
Given this access, setup the remote client,

@@

Login to the UI and copy the URI of the workflow or task whose inputs and outputs you want to review, and provide these to the `get` method of the remote client,

```{python}
# | label: get-workflow-io
workflow_inputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-argo-nix-bui-5c9ebf8-dev-1hk-d5805de62e8044f79d4/f26c1pjy-0-dn0/i"
)
postprocessing_outputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-argo-nix-bui-5c9ebf8-dev-1hk-d5805de62e8044f79d4/f26c1pjy-0-dn0-0-dn6/o"
)
```

This will not download the results but will provide a summary of the outputs.

@@

Download the results you would like to review,

@@

In this example, we load the postprocessed data from the downloaded file,

@@

as well as the posterior samples,

@@

In this case, we extract the gene selection data by cooptimizing MAE and correlation between spliced expression levels and estimates of temporal ordering

@@

Here we re-generate the gene selection summary plot.

@@

Of course, you can generate any plot of interest relevant to the loaded data.
See the [plots package source](https://github.com/pinellolab/pyrovelocity/tree/main/src/pyrovelocity/plots), [plots API reference](../../reference/plots.qmd), and the guide for the [workflow summarization task](https://github.com/pinellolab/pyrovelocity/blob/main/src/pyrovelocity/tasks/summarize.py) for ideas regarding built-in or custom plots.

>>>>

---
title: Pancreatic endocrinogenesis
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

@@

Please see the [guide on interactive results review](/guides/interactive/interactive.qmd) for a 
general review of how to download and review results. Here we use the same 
approach without any of the explanatory text to retrieve model results to 
generate plots for model selection and evaluation

@@

::: {#wrn-downsampled-data .callout-warning collapse=true title="Downsampled Data"}
In this notebook we illustrate how to download and review results using
unrealistic downsampled data. Therefore, this notebook should not be taken
to represent the results of applying the model to real data.
:::

@@

@@

```{python}
# | label: get-workflow-io
workflow_inputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a/f26c1pjy-0-dn1-0-dn6/i"
)
postprocessing_outputs = remote.get(
    "flyte://v1/pyrovelocity/development/pyrovelocity-py311-defaul-fe20d09-dev-pzh-17b5092261c84e8695a/f26c1pjy-0-dn1-0-dn6/o"
)
```

@@

@@

@@

@@

@@

@@
